\documentclass[a4paper,twocolumn]{article}
\usepackage[ngerman]{babel}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{fontenc}
\usepackage{color}
\usepackage{soul}
\usepackage{soulutf8}

\setlist{nolistsep}

% Allows fancy stuff in the page header
\usepackage{fancyhdr}
\pagestyle{fancy}

% multirow and multicol
\usepackage{multirow}
\usepackage{multicol}
\columnsep24pt
\columnseprule0.1pt

% parindent
\parindent0px
\parskip3pt

\geometry{top=1cm, headsep=0pt,headheight=0.5cm, % top part
bottom=1cm, footskip=0.5cm, % bottom part
left=0.4cm,right=0.4cm} % left / right part

% fancy header
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\headwidth}{\textwidth}

\tabcolsep=0.1cm

% Redefine section commands to use less space
\makeatletter
\renewcommand{\section}{\@startsection{section}{1}{0mm}%
                                {-1ex plus -.5ex minus -.2ex}%
                                {0.5ex plus .2ex}%x
                                {\normalfont\large\bfseries}}
\renewcommand{\subsection}{\@startsection{subsection}{2}{0mm}%
                                {-1explus -.5ex minus -.2ex}%
                                {0.5ex plus .2ex}%
                                {\normalfont\normalsize\bfseries}}
\renewcommand{\subsubsection}{\@startsection{subsubsection}{3}{0mm}%
                                {-1ex plus -.5ex minus -.2ex}%
                                {1ex plus .2ex}%
                                {\normalfont\small\bfseries}}
\makeatother

\usepackage{empheq}
\begin{document}
\twocolumn
\newpage
\setcounter{page}{1}
\pagestyle{plain}

\section{OSI model}
\begin{table}[h]
\begin{tabular}{llll}
\textbf{Nr} & \textbf{Name} & \textbf{Protocols}      & \textbf{Data Unit} \\ \hline
7           & Application   & HTTP, FTP, SMTP         & Data               \\ \hline
6           & Presentation  & SSL/TLS, MIME           & Data               \\ \hline
5           & Session       & SOCKS, RPC, PAP         & Data               \\ \hline
4           & Transport     & TCP, UDP                & Segment            \\ \hline
3           & Network       & IPv4, IPv6, IPsec, ICMP & Packet/Datagram    \\ \hline
2           & Data Link     &                         & Bit/Frame          \\ \hline
1           & Physical      &                         & Bit                \\ \hline
\end{tabular}
\end{table}

\section{SSL/TLS Key Exchange}
\begin{description}
\item[RSA Key Exchange (case 1)]: client creates pre-master secret for session and sends it encrypted with server's public key to server. Secure against active/passive attacks, no PFS, no contributory key agreement.

\item[RSA Key Exchange (case2)]: server has RSA key that can only sign. Create temporary public/private keypair that is used to exchange a client generated key. Secure against active/passive attacks, PFS, no contributory key agreement.

\item[Anonymous Diffie-Hellman] uses Diffie-Hellman, but without authentication. Because the keys used in the exchange are not authenticated, the protocol is susceptible to Man-in-the-Middle attacks. Provides Perfect Forward Secrecy (PFS). Not secure against passive attacks. Contributory key agreement.

\item[Fixed Diffie-Hellman] embeds the server's public Diffie-Hellman parameter in the certificate, and the CA then signs the certificate. That is, the certificate contains the Diffie-Hellman public-key parameters, and those parameters never change. Secure against passive/active attacks, no PFS, contributory key agreement.

\item[Ephemeral Diffie-Hellman] uses temporary, public keys. Each instance or run of the protocol uses a different public key. The authenticity of the server's temporary key can be verified by checking the signature on the key. Secure against passive/active attacks, PFS, contributory key agreement.
\end{description}

\end{document}